***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2015-10-13 Schloss_Cluster_PeerJ_2015.Rmd
Does printbibliography work?
Change scipen
Turn off scientific notation
Turn off caching and name chunks

```{r knitr.settings, eval=TRUE, echo=FALSE, cache=TRUE}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

options(scipen=999999999)

inline_hook <- function(x){
  if(is.numeric(x)){
    paste(format(x,big.mark=',', digits=2))
  }
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

## Results and Discussion
```{r}
he_stability <- read.table(file="data/process/he.mcc_ref.summary", header=T)
```

@@

```{r, cache=TRUE}
n_overlap <- read.table(file="data/gg_13_8/gg_13_8_97.overlap.count", row.names=1)
n_v4_overlap <- n_overlap["v4", 1]
n_v9_overlap <- n_overlap["v9", 1]
n_v19_total <- n_overlap["v19", 1]

miseq_info <- read.table(file="data/miseq/miseq.seq.info", row.names=1)
n_groups <- miseq_info["n_groups",1]
n_miseq_seqs <- miseq_info["n_miseq_seqs",1]
n_unique_miseq_seqs <- miseq_info["n_unique_miseq_seqs",1]

@@

```{r, cache=TRUE}
small_dists <- read.table(file="data/gg_13_8/gg_13_8_97.small_dist.count", row.names=1)
n_small_v4_dist <- small_dists["v4",1]
n_small_v19_dist <- small_dists["v19",1]

@@

\bibliography

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

inline_hook <- function(x){
  if(is.numeric(x)){
    paste(format(x,big.mark=',', digits=2, scientific=FALSE))
  }
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

## Results and Discussion
```{r he_stability_analysis}
he_stability <- read.table(file="data/process/he.mcc_ref.summary", header=T)
```

@@

```{r region_overlap}
n_overlap <- read.table(file="data/gg_13_8/gg_13_8_97.overlap.count", row.names=1)
n_v4_overlap <- n_overlap["v4", 1]
n_v9_overlap <- n_overlap["v9", 1]
n_v19_total <- n_overlap["v19", 1]
```

```{r miseq_analysis}
miseq_info <- read.table(file="data/miseq/miseq.seq.info", row.names=1)
n_groups <- miseq_info["n_groups",1]
n_miseq_seqs <- miseq_info["n_miseq_seqs",1]
n_unique_miseq_seqs <- miseq_info["n_unique_miseq_seqs",1]

@@

```{r database_analysis}
small_dists <- read.table(file="data/gg_13_8/gg_13_8_97.small_dist.count", row.names=1)
n_small_v4_dist <- small_dists["v4",1]
n_small_v19_dist <- small_dists["v19",1]

@@
